My title

### 2024-11-04 paper/paper.qmd
updated paper

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
```

@@

@@

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

@@

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Yisu Hou
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
header-includes:
  - \usepackage{float}
  - \usepackage{placeins}
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(caret)
library(glmnet)
library(nnet)
library(lubridate)
library(pROC)
library(stringr)
```

@@

note: For the literature review/why our thing matters section talk about how other predictions don't consider the biases in polls. Our thing is something new because we attempt to account for the bias in historical predictions for our 2024 prediction. (basically, for all models and predictions, I have an adjusted version that adjusts the support percentage using the difference between 2020 polls and real election outcomes, and a normal version that just uses the percentages from 2024 polls)

There's essentially 3 different levels of analysis: using multiple linear regression to look at the candidates' support over time on the national level, using logistic regression to predict the chance of winning on the national level, using state polls data to see who is ahead in electoral college votes.

@@

## Outcome variable

The outcome variable is the level of support for the two leading US presidential candidates, Vice President Kamala Harris and Former President Donald Trump, recorded as a percentage of likely voters. For the national-level analysis, the support percentage represents the percentage of polled individuals who responded in favor of a specific candidate to a question that asked about their preferred presidential candidate in a national-level poll. For the regional datasets, the support percentage represents the percentage of likely voters who preferred a specific candidate in a poll that targets a specific state or congressional district of the United States. @fig-outcome shows the distribution of support percentages in the aggregated polling data from 2020 and 2024 presidential elections.

```{r}
#| echo: false
#| message: false
#| warning: false

trump_2024 <- read_csv(here::here("data/02-analysis_data/trump_2024_analysis_data.csv"))
harris_2024 <- read_csv(here::here("data/02-analysis_data/harris_2024_analysis_data.csv"))
trump_2024_lower <- 
  read_csv(here::here("data/02-analysis_data/trump_2024_analysis_data_lower.csv"))
harris_2024_lower <- 
  read_csv(here::here("data/02-analysis_data/harris_2024_analysis_data_lower.csv"))
trump_2020 <- read_csv(here::here("data/02-analysis_data/trump_2020_analysis_data.csv"))
biden_2020 <- read_csv(here::here("data/02-analysis_data/biden_2020_analysis_data.csv"))

# aggregated dataset for summary statistics
# datasets with lower numeric scores already includes polls with a score of 3.0
all_combined <- bind_rows(harris_2024_lower, trump_2024_lower,
    biden_2020, trump_2020)

```

```{r}
#| label: fig-outcome
#| fig-cap: Percentage Support in US Presidential Polls
#| echo: false
#| message: false
#| warning: false

ggplot(all_combined, aes(x = pct)) +
  geom_histogram(
    binwidth = 1,                # Adjust bin width for granularity
    fill = "#2c7bb6",            # Aesthetic fill color (steel blue)
    color = "white",             # Border color for bins
    alpha = 0.8                   # Transparency of the fill
  ) +
  labs(
    x = "Percentage Support",
    y = "Number of Polls"
  ) +
  theme_minimal(base_size = 14) +   # Minimal theme with increased base font size
  theme(
    plot.title = element_text(
      size = 16, 
      face = "bold", 
      hjust = 0.5,                # Center the title
      margin = margin(b = 10)     # Add space below the title
    ),
    plot.subtitle = element_text(
      size = 12, 
      hjust = 0.5, 
      margin = margin(b = 20)     # Add space below the subtitle
    ),
    axis.title = element_text(face = "bold"), # Bold axis titles
    axis.text = element_text(color = "gray30"), # Dark gray axis text
    panel.grid.major = element_line(color = "gray80"), # Light gray major grid lines
    panel.grid.minor = element_blank()                 # Remove minor grid lines
  ) +
  # Add a vertical line for the mean percentage support
  geom_vline(
    aes(xintercept = mean(pct, na.rm = TRUE)),
    color = "#d73027",           # Aesthetic color (red)
    linetype = "dashed", 
    size = 1
  ) +
  # Annotate the mean value on the plot
  annotate(
    "text",
    x = mean(all_combined$pct, na.rm = TRUE) - 7, # Position text slightly to the right of the mean line
    y = Inf,                                     # Position text at the top of the plot
    label = paste("Mean:", round(mean(all_combined$pct, na.rm = TRUE), 1), "%"),
    vjust = 2,                                   # Vertical adjustment
    color = "#d73027",
    size = 5,
    fontface = "bold"
  )

```

\FloatBarrier

The aggregated polling data includes support percentages of different presidential candidates in polls with different FiveThirtyEight ratings [CITATION HERE https://abcnews.go.com/538/best-pollsters-america/story?id=105563951] across two elections. Please view [UPDATE APPENDIX] for summary statistics of sub-datasets.

As displayed by @fig-outcome, the distribution of support percentages is close to a normal distribution, with most data points between 45 and 52 percent.

@@

### End Date
```{r}
#| label: fig-dates-past
#| fig-cap: Distribution of Poll End Date, 2020 Cycle
#| echo: false
#| message: false
#| warning: false

ggplot(all_combined %>% filter(cycle == 2020), aes(x = end_date)) +
  geom_histogram(binwidth = 7, fill = "#1f78b4", color = "white", alpha = 0.7) +
  labs(
    x = "End Date",
    y = "Number of Polls"
  ) +
  scale_x_date(date_labels = "%b %d, %Y", date_breaks = "1 month") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

```
\vspace{1em}
\FloatBarrier

```{r}
#| label: fig-dates-current
#| fig-cap: Distribution of Poll End Date, 2024 Cycle
#| echo: false
#| message: false
#| warning: false

ggplot(all_combined %>% filter(cycle == 2024), aes(x = end_date)) +
  geom_histogram(binwidth = 7, fill = "#1f78b4", color = "white", alpha = 0.7) +
  labs(
    x = "End Date",
    y = "Number of Polls"
  ) +
  scale_x_date(date_labels = "%b %d, %Y", date_breaks = "1 month") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

```
\FloatBarrier

### Sponsored

```{r}
#| label: fig-sponsored
#| fig-cap: Number of Polls with and without Sponsors
#| echo: false
#| message: false
#| warning: false

ggplot(all_combined, aes(x = factor(has_sponsor, levels = c(0,1), labels = c("No Sponsor", "Has Sponsor")))) +
  geom_bar(fill = "#1f78b4", color = "white", alpha = 0.7) +
  labs(
    x = "Has Sponsor",
    y = "Number of Polls"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold")
  )

```

\FloatBarrier

### Transparency Score

```{r}
#| label: fig-transparency
#| fig-cap: Distribution of Transparency Scores
#| echo: false
#| message: false
#| warning: false

ggplot(all_combined, aes(x = factor(transparency_score))) +
  geom_bar(fill = "#1f78b4", color = "white", alpha = 0.7) +
  labs(
    x = "Transparency Score",
    y = "Number of Polls"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold")
  )

```

\FloatBarrier

### Sample Size

```{r}
#| label: fig-sample
#| fig-cap: Distribution of Sample Sizes
#| echo: false
#| message: false
#| warning: false

ggplot(all_combined, aes(x = sample_size)) +
  geom_histogram(binwidth = 500, fill = "#1f78b4", color = "white", alpha = 0.7) +
  labs(
    x = "Sample Size",
    y = "Number of Polls"
  ) +
  scale_x_continuous(labels = scales::comma) +
  coord_cartesian(xlim = c(0, 6000)) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold")
  )

```

\FloatBarrier

@@

```{r}

```

```{r}

```

@@

```{r}

```

@@

```{r}

```
